PHAT RAID, yo

### 2014-05-15 paper/paper.tex
future work

\begin{figure}
  \centering
  \begin{tikzpicture}
    [<->,scale=.85,shorten <=2pt, shorten >=2pt,]
    \node [rectangle, draw, thick, inner sep=5pt] (raidclient) at (0,2) {Raid Client};
    \node [rectangle, draw, thick, inner sep=5pt] (client1) at (-4,1) {Client 1};
    \node [rectangle, draw, thick, inner sep=5pt] (client2) at (0,0) {Client 2};
    \node [rectangle, draw, thick, inner sep=5pt] (client3) at (4,1) {Client 3};
    \node [rectangle, draw, thick, inner sep=5pt] (vr11) at (-6, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr12) at (-4, -2) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr13) at (-2, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr21) at (-2, -4) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr22) at (0, -4) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr23) at (2, -4) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr31) at (2, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr32) at (4, -2) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr33) at (6, -2) {Replica};

@@

>>>>

\begin{figure}
\hspace*{-.43in}
  \centering
  \begin{tikzpicture}
    [<->,scale=.85,shorten <=2pt, shorten >=2pt,]
    \node [rectangle, draw, thick, inner sep=5pt] (raidclient) at (0,2) {Raid Client};
    \node [rectangle, draw, thick, inner sep=5pt] (client1) at (-4,1) {Client 1};
    \node [rectangle, draw, thick, inner sep=5pt] (client2) at (0,0) {Client 2};
    \node [rectangle, draw, thick, inner sep=5pt] (client3) at (4,1) {Client 3};
    \node [rectangle, draw, thick, inner sep=5pt] (vr11) at (-6, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr12) at (-4, -2) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr13) at (-2, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr21) at (-2, -4) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr22) at (0, -4) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr23) at (2, -4) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr31) at (2, -2) {Replica};
    \node [rectangle, draw, thick, inner sep=5pt] (vr32) at (4, -2) {Master};
    \node [rectangle, draw, thick, inner sep=5pt] (vr33) at (6, -2) {Replica};

@@

We would like to perform a real evaluation rather than a simulation. 
It seems that as file size increases, PhatRaid becomes more appealing 
for lower commit latency. It is not clear from our
simulation, however, when the file size is small enough for other effects (such as
network latency, communications overhead) to become more important. And, as a 
result, PhatRaid having no improvements (or possibly worse performance).
